Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
removed red comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system. We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house. The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}. \textcolor{red}{However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), what indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.}
%\begin{figure}[h]
%\includegraphics[width=0.65\textwidth]{loadcurve.png}
%\centering
%\caption{Five weeks monitored load curve from House 1.}
%\label{fig:loadcurve}
%\end{figure}

>>>>

In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system. We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house. The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}. However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
%\begin{figure}[h]
%\includegraphics[width=0.65\textwidth]{loadcurve.png}
%\centering
%\caption{Five weeks monitored load curve from House 1.}
%\label{fig:loadcurve}
%\end{figure}
